---
title: "RWorksheet_Gonzaga#3b"
author: "SHAMEL GONZAGA"
date: "2024-10-02"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1
# A.
```{r}
df <- data.frame(
  Respondents = 1:20, 
  Sex = c(2, 2, 1, 2, 2, 2, 2, 2, 2, 2, 1, 2, 2, 2, 2, 2, 2, 2, 1, 2), 
  FathersOccupation = c(1, 3, 3, 3, 1, 2, 3, 1, 1, 1, 3, 2, 1, 3, 3, 1, 3, 1, 2, 1), 
  PersonsAtHome = c(5, 7, 3, 8, 5, 9, 6, 7, 8, 4, 7, 5, 4, 7, 8, 8, 3, 11, 7, 6), 
  SiblingsAtSchool = c(6, 4, 4, 1, 2, 1, 5, 3, 1, 2, 3, 2, 5, 5, 2, 1, 2, 5, 3, 2), 
  TypesOfHouses = c(1, 2, 3, 1, 1, 3, 3, 1, 2, 3, 2, 3, 2, 2, 3, 3, 3, 3, 3, 2)
)
df
```

# B.

```{r}
str(df)
```
# The structure represents quantity of objects and variables in the data frame. It provides the initial few contents of the dataframe along with the data type of every column. 

# C.

```{r}
mean(df$SiblingsAtSchool)
```

# D.

```{r}
subset<- df[1:2, ]
subset 
```

# E.

```{r}
subSetOne <- df[c(3, 5), c(2, 4)]
subSetOne
```

# F. 

```{r}
types.houses <- df$TypesOfHouses   
```

# G.

```{r}
maleFarmers <- subset(df, Sex == 1 & FathersOccupation == 1)
maleFarmers
```

# H.

```{r}
femaleSiblings <- subset(df, Sex == 2 & SiblingsAtSchool >= 5)
femaleSiblings
```

# 2.

```{r}
df = data.frame(Ints=integer(),
          Doubles=double(), Characters=character(),
          Logicals=logical(),
          Factors=factor(),
          stringsAsFactors=FALSE)

print("Structure of the empty dataframe:")
print(str(df))
```

# A.

#Looking at the result it will shows the structure of the empty data frame. As depicted therein, it has 0 observations and 5 variables. It also displays different data types with no data yet

# 3.
# A.

```{r}
HouseHold <- read.csv("HouseholdData.csv")
HouseHold
```

# B.

```{r}
HouseHold$Sex <- as.integer(factor(HouseHold$Sex,
                   levels = c("Male", "Female"),
                   labels = c(1, 2)))
HouseHold
```

# C.

```{r}
HouseHold$Types.of.Houses <- as.integer(factor(HouseHold$Types.of.Houses, levels = c("Wood", "Congrete", "Semi-congrete"), labels = c(1, 2, 3)))
HouseHold
```

# D.

```{r}
HouseHold$Fathers_Occupation <-  as.character(factor(HouseHold$Fathers.Occupation, levels = c(1, 2, 3), labels = c("Farmer", "Driver", "Others")))
HouseHold$Fathers_Occupation
```

# E.

```{r}
femaleDriver <- subset(HouseHold, Sex == 2 & Fathers_Occupation == "Driver")
femaleDriver
```

# F.

```{r}
SiblingSchool <- subset(HouseHold, Siblings.at.School >= 5)
SiblingSchool
```

# 4. 

# The graph analysis of the tweet reveals that the highest number of the tweets per day from July 14, 2020 to July 21, 2020 has shown negative. The second highest percentage is positive while the lowest percentage of sentiments of tweets per day is neutral.
