---
title: "RWorksheet_Gonzaga#1"
author: "Shamel"
date: "2024-09-03"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
age <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 42, 53, 41, 51, 35, 24, 33, 41)
```

a. How many data points?

```{r}
length(age)
```
b. Write the R code and its output.

age <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 42, 53, 41, 51, 35, 24, 33, 41)

2. Find the reciprocal of the values for age.
  Write the R code and its output.
```{r}
reciprocal <- 1/age
print(reciprocal)
```
3. Assign also new_age <- c(age, 0, age)
What happen to the new_age?
  
```{r}
new_age <- c(age, 0, age)
print(new_age)
```
When printed, it shows 

4. Sort the values of age.
Write the R code and its output.

```{r}
sorted_age <- sort(age)
sorted_age
```

5. Find the minimum and maximum value for age.
Write the R code and its output.

```{r}
min_age <- min(age)
max_age <- max(age)
print (min_age)
print (max_age)
```
6. Set up a vector named data, consisting of 2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5, 2.3, 2.5, 2.3, 2.4, and 2.7.

```{r}
data <- c(2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5, 2.3, 2.5, 2.3, 2.4, 2.7)
```
a. How many data points?

```{r}
length(data)
```
b. Write the R code and its output 

```{r}
data <- c(2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5, 2.3, 2.5, 2.3, 2.4, 2.7)
```

7. Generates a new vector for data where you double every value of the data. | What happen to the data?
```{r}
doubled_data <- 2 * data
doubled_data
```

8. Generate a sequence for the following scenario:

8.1 Integers from 1 to 100.
```{r}
int_seq <- seq(1, 100)
int_seq
```
8.2 Numbers from 20 to 60
```{r}
num_seq <- seq(20, 60)
num_seq
```

