---
title: "RWorksheets_Gonzaga#2.R"
output: pdf_document
date: "2024-09-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Using Vectors**\
1. Create a vector using : operator\

      a. Sequence from -5 to 5. Write the R code and its output.
        Describe its output.

```{r}
vec <- -5:5
print(vec)
```
A series of integers between -5 and 5 is the output. An integer sequence created using the : operator. It creates a vector in this case, increasing by 1 each step, starting at -5 and ending at 5. 

      b. x <- 1:7. What will be the value of x?
```{r}
x <- 1:7
print(x)
```

2.* Create a vector using seq() function a. seq(1, 3, by=0.2) # specify step size Write the R script and its output. Describe the output.

```{r}
x <- seq(1, 3, by=0.2)
print(x)
```

The function creates a sequence of numbers starting from 1 and it will at 3, with each size of 0.2. So the output vector containing a numbers from 1.0 to 3.0 which is incremented by 0.2.

3. A factory has a census of its workers. There are 50 workers in total. The following
list shows their ages: 34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35, 24,33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18.

```{r}
ages <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27,
          22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37,
          43, 53, 41, 51, 35, 24, 33, 41, 53, 40, 18, 44, 38,
          41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18)

```
      a. Access 3rd element, what is the value?

```{r}
ages[3]
```
      b. Access 2nd and 4th element, what are the values?
```{r}
ages[c(2,4)]
```
      c. Access all but the 4th and 12th element is not included. Write the R script and its output.
```{r}
ages[-c(4,12)]
```
4.Create a vector . Then named the vector, names(x).\

      a. Print the results. Then access x[c("first", "third")]. Describe the output.
```{r}
x <- c("first" = 3, "second" = 0, "third" = 9)
x
```
We can access only the named elements "first" and "third". The output is a sub-vector containing the values 3 and 9 from the original vector x. \

      b. Write the code and its output.
```{r}
(x[c("first", "third")])
```
5. Create a sequence x from -3:2.\
      a. Modify 2nd element and change it to 0;
        x[2] <- 0
        x
        Describe the output.\
        - When it modify the 2nd element using x[2] <- 0, the -2 at the 2nd position is replaced by 0. The new vector becomes -3 0 -1 0 1 2.
      b. Write the code and its output.\
```{r}
x <- -3:2
x[2] <- 0
print(x)
```
6. The following data shows the diesel fuel purchased by Mr. Cruz.\
        a. Create a data frame for month, price per liter (php) and purchase-quantity (liter). Write the R scripts and its output.
```{r}
month <- c("Jan", "Feb", "March", "Apr", "May", "June")
price_per_liter <- c(52.50, 57.25, 60.00, 65.00, 74.25, 54.00)
purchase_quantity <- c(25, 30, 40, 50, 10, 45)

fuel_data <- data.frame(Month = month, Price_per_Liter = price_per_liter, Purchase_Quantity = purchase_quantity)
print(fuel_data)

```
        b. What is the average fuel expenditure of Mr. Cruz from Jan to June? Note: Use ‘weighted.mean(liter, purchase)‘. Write the R scripts and its output.
```{r}
average_fuel_expenditure <- weighted.mean(price_per_liter, purchase_quantity)
print(average_fuel_expenditure)
```