---
title: "RWorksheet_Gonzaga#4a.Rmd"
author: "SHAMEL GONZAGA"
date: "2024-10-16"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Data Frame about shoe size and height.

#a
```{r}
shoe_size <- c(6.5, 9.0, 8.5, 8.5, 10.5, 7.0, 9.5, 9.0, 13.0, 7.5, 10.5, 8.5, 
               12.0, 10.5, 13.0, 11.5, 8.5, 5.0, 10.0, 6.5, 7.5, 8.5, 10.5, 8.5, 
               10.5, 11.0, 9.0, 13.0)

height <- c(66.0, 68.0, 64.5, 65.0, 70.0, 64.0, 70.0, 71.0, 72.0, 64.0, 74.5, 
            67.0, 71.0, 71.0, 77.0, 72.0, 59.0, 62.0, 72.0, 66.0, 64.0, 67.0, 
            73.0, 69.0, 72.0, 70.0, 69.0, 70.0)

gender <- c('F', 'F', 'F', 'F', 'M', 'F', 'F', 'F', 'M', 'F', 'M', 'F', 'M', 
            'M', 'M', 'M', 'F', 'F', 'M', 'F', 'F', 'M', 'M', 'F', 'M', 'M', 
            'M', 'M')

data1<- data.frame(
  Shoe_Size = shoe_size,
  Height = height,
  Gender = gender
)

```
output shows the tabular data of shoe size which consist the shoe sizes of 29 
individuals, height consists the height in inches, and gender consists the 
gender of the individuals where 'M' represents the males and 'F' the females.

#b

```{r}
male_subset <- subset(data1, gender == 'M', select = c(Shoe_Size, Height))
male_subset

female_subset <- subset(data1, gender == 'F', select = c(Shoe_Size, Height))
female_subset
```

#c

```{r}
mean(data1$Shoe_Size)
mean(data1$Height)
```

#d

A positive correlation nearing the value of 1 exemplifies that there exists a 
positive relationship – as the size of a shoe increases, usually, the height 
goes up too.


#2. 

```{r}
months_vector <- c(
  "March", "April", "January", "November", "January", "September", 
  "October", "September", "November", "August", "January", 
  "November", "November", "February", "May", "August", "July", 
  "December", "August", "August", "September", "November", 
  "February", "April"
)
factor_months_vector <- factor(months_vector)
factor_months_vector

levels(factor_months_vector)
```

#3. 

```{r}
summary(months_vector)
summary(factor_months_vector)
```

The factor version (factor_months_vector) is more beneficial for categorical 
data such as months because it transforms and tally’s the specific levels 
(months) at once. The character vector (months) are less effective in this case 
because it doesn’t provide any sense of aggregation of the data. Rather, it just 
considers the months as separate single text values

The number of elements and character vector (months) will have been accomplished 
by using the summary() on the character vector. This will be obtained with the 
help of the summary() function applied to the factor called factor_months_vector, 
which will offer the frequency of each level in the data base, or in other words, 
it will show how many times each month was mentioned in the data set.

#4.

```{r}
direction <- c("East", "West", "North")
frequency <- c(1, 4, 3)

new_order_data <- factor(direction, levels = c("East","West","North"))
print(new_order_data)
```

#5.

#a.
```{r}
file1 <- read.table("import_march.csv", header = TRUE, sep = ",")
```

#b.
```{r}
print(file1)
```

#6 Full Search

#a.

```{r}
e_search <- function(user_input){ if (user_input < 1 | user_input > 50) {
  print("The number selected is beyond the range of 1 to 50")
  }else if (user_input == 20){
    print("TRUE")
  }else{
    print(user_input)
  }
}

user_input <- readline(prompt = "Select a number from 1 - 50: ")
e_search(user_input)

```

#7 Change

```{r}
minimum_bills <- function(price){
  bills <- c(1000, 500, 200, 100, 50)
  total_bills <- 0
  
  for (bill in bills) {
    count <- floor(price / bill)
    price <- price - count * bill
    total_bills <- total_bills + count
  }
  
  return(total_bills)
}

price <- as.numeric(readline(prompt = "Enter the price of the snack: "))
print(paste("Minimum number of bills needed to purchase a snack:", minimum_bills(price)))
```

#8

#a

```{r}
name <- c("Annie", "Thea", "Steve", "Hanna")
grade1 <- c(85, 65, 75, 95)
grade2 <- c(65, 75, 55, 75)
grade3 <- c(85, 90, 80, 100)
grade4 <- c(100, 90, 85, 90)

student_grade <- data.frame(
  Name = name,
  Grade1 = grade1, 
  Grade2 = grade2,
  Grade3 = grade3,
  Grade4 = grade4
)
student_grade
```

#b

```{r}
for (i in 1:4) {
  total <- sum(student_grade[i, 2:5])  
  average <- total / 4
  
  if (average > 90){
    print(paste0(student_grade[i, 1], "'s average grade this semester is ", average))
  }
}
```

#c
```{r}
for (i in 2:4){
  total <- 0
  for (j in 1:4){
    total <- total + student_grade[j, i]
  }
  
  average <- total / 4
  
  if (average < 80){
    print(paste("The", colnames(student_grade[i]), "test was difficult"))
  }
}
```

#d

```{r}
for (j in 1:nrow(student_grade)) {  
  highest <- student_grade[j, 2]
  
  for (i in 3:ncol(student_grade)) { 
    if (student_grade[j, i] > highest) {
      highest <- student_grade[j, i]  
    }
  }
 
  if (highest > 90){
    print(paste0(student_grade[j, 1], "'s grade this semester is ", highest))
  }
}
```

