---
title: "RWorksheets_Gonzaga#2.R"
author: "Shamel Grace G. Gonzaga"
output: html_document
date: "2024-09-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Using Vectors**\
1. Create a vector using : operator\

  a. Sequence from -5 to 5. Write the R code and its output.
      Describe its output.

```{r}
vec <- -5:5
print(vec)
```
A series of integers between -5 and 5 is the output. An integer sequence created using the : operator. It creates a vector in this case, increasing by 1 each step, starting at -5 and ending at 5. 

  b. x <- 1:7. What will be the value of x?
```{r}
x <- 1:7
print(x)
```

2.* Create a vector using seq() function a. seq(1, 3, by=0.2) # specify step size Write the R script and its output. Describe the output.

```{r}
x <- seq(1, 3, by = 0.2)
x
```

The function creates a sequence of numbers starting from 1 and it will at 3, with each size of 0.2. So the output vector containing a numbers from 1.0 to 3.0 which is incremented by 0.2.

3. A factory has a census of its workers. There are 50 workers in total. The following
list shows their ages: 34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35, 24,33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18.

```{r}
ages <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27,
          22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37,
          43, 53, 41, 51, 35, 24, 33, 41, 53, 40, 18, 44, 38,
          41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18)

```
  a. Access 3rd element, what is the value?

```{r}
ages[3]
```
  b. Access 2nd and 4th element, what are the values?
```{r}
ages[c(2,4)]
```
  c. Access all but the 4th and 12th element is not included. Write the R script and its output.
```{r}
ages[-c(4,12)]
```
4.Create a vector . Then named the vector, names(x).\

  a. Print the results. Then access x[c("first", "third")]. Describe the output.
```{r}
x <- c("first" = 3, "second" = 0, "third" = 9)
x
```
We can access only the named elements "first" and "third". The output is a sub-vector containing the values 3 and 9 from the original vector x. \

  b. Write the code and its output.
```{r}
(x[c("first", "third")])
```
5. Create a sequence x from -3:2.\
      a. Modify 2nd element and change it to 0;
        x[2] <- 0
        x
        Describe the output.\
        - When it modify the 2nd element using x[2] <- 0, the -2 at the 2nd position is replaced by 0. The new vector becomes -3 0 -1 0 1 2.
      b. Write the code and its output.\
```{r}
x <- -3:2
x[2] <- 0
print(x)
```
6. The following data shows the diesel fuel purchased by Mr. Cruz.\
        a. Create a data frame for month, price per liter (php) and purchase-quantity (liter). Write the R scripts and its output.
```{r}
mrCruzdata <- data.frame(
  Month = c("Jan", "Feb", "Mar", "Apr", "May", "Jun"),
  Price_Per_Liter = c(52.50, 57.25, 60.00, 65.00, 74.25, 54.00),
  Purchase_Quantity = c(25, 30, 40, 50, 10, 45)
)
mrCruzdata
```
    b. What is the average fuel expenditure of Mr. Cruz from Jan to June? 
Note: Use ‘weighted.mean(liter, purchase)‘. Write the R scripts and its output.
```{r}
average_fuel <- weighted.mean(mrCruzdata$Price_Per_Liter, mrCruzdata$Purchase_Quantity)
average_fuel
```
7. R has actually lots of built-in datasets. For example, the rivers data “gives
the lengths (in miles) of 141 “major” rivers in North America, as compiled by 
the US Geological Survey”.
      a. Type “rivers” in your R console.
Create a vector data with 7
elements, containing the number of elements (length)
in rivers, their sum (sum), mean (mean),
median(median), variance(var), standard deviation(sd),
minimum (min) and maximum (max).
      b. What are the results?
    - The length of the dataset is 141, meaning it includes data for 141 rivers. 
    The sum of all river lengths is 83,357 miles, showing the total length of all the rivers combined. The mean river length is approximately 591.18 miles, indicating the average length of the rivers in the dataset. The median river length is 425 miles, meaning that half of the rivers are shorter than 425 miles and half are longer. The variance, which measures the spread of the river lengths from the mean, is approximately 243,908.41. The standard deviation is about 493.87 miles, showing how much individual river lengths tend to deviate from the mean. The minimum length which is the shortest river in the dataset is 135 miles long, while the maximum value is the longest river is 3,710 miles long.\
        c. Write the R scripts and its outputs.
```{r}
rivers

data <- c(length(rivers), sum(rivers), mean(rivers), median(rivers), var(rivers), 
          sd(rivers), min(rivers), max(rivers))

data
```

8.
  a. Create vectors according to the above table. Write the R scripts and its output.
```{r}
power_ranking <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 
                   11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 
                   21, 22, 23, 24, 25)

celebrity_name <- c("Tom Cruise", "Rolling Stones", "Oprah Winfrey", "U2", "Tiger Woods",
                    "Steven Spielberg", "Howard Stern", "50 Cent", "Cast of the Sopranos",
                    "Dan Brown", "Bruce Springsteen", "Donald Trump", "Muhammad Ali",
                    "Paul McCartney", "George Lucas", "Elton John", "David Letterman",
                    "Phil Mickelson", "J.K. Rowling", "Bradd Pitt", "Peter Jackson",
                    "Dr. Phil McGraw", "Jay Leno", "Celine Dion", "Kobe Bryant")

pay <- c(67, 90, 225, 110, 90, 332, 302, 41, 52, 88, 
         55, 44, 55, 40, 233, 34, 40, 47, 75, 25, 
         39, 45, 32, 40, 31)

power_ranking
celebrity_name
pay
```
  b. Modify the power ranking and pay of J.K. Rowling. Change power ranking to 15 and pay to 90. Write the R scripts and its output.
```{r}
celebrity_name[19] <- "J.K Rowling"
power_ranking[19] <- 15
pay[19] <- 90

print(power_ranking[19])
print(pay[19])
```
c. Create an excel file from the table above and save it as csv file(PowerRanking). Import the csv file into the RStudio. What is the R script?
```{r}
data_forbes <- read.csv("PowerRanking.csv")
data_forbes
```
d. Access the rows 10 to 20 and save it as Ranks.RData. Write the R script and its output.
```{r}
rdata <- data_forbes[10:20, ]

save(rdata, file = "Ranks.RData")

rdata

```      
e. Describe its output
- It displays the rows 10 to 20 data, showing the power ranking, celebrity name and pay for each which the data includes celebrities like J.K. Rowling with her updated data ranking and pay which modified from the letter b. It is saved as an .Rdata file.


9.
  a. Import the excel file into your RStudio. What is the R script?
```{r}
library(openxlsx)
vienna <- read.xlsx("hotels-vienna.xlsx")
```        
  b. How many dimensions does the dataset have? What is the R script? WHat is its output?
```{r}
dim(vienna)
```        
  c. Select columns country, neighbourhood, price, stars, accomodation_type, and ratings. Write the R script.
```{r}
sel_col <- vienna[, c("country", "neighbourhood", "price", "stars", "accommodation_type", "rating")]
```        
d. Save the data as **new.RData to your RStudio. Write the R script.
```{r}
save(sel_col, file = "new.RData")
```   
e. Display the first six rows and last six rows of the new.RData. What is the R script?
```{r}
load("new.RData")
head(sel_col)
tail(sel_col)
```   
10. Create a list of ten (10) vegetables you ate during your lifetime. If none, just list down.
a. Write the R scripts and its output.
```{r}
gulay <- list("Okra", "Repolyo", "Kamote", "Kangkong", "Kalabasa", "Pechay", "Pipino", "Patatas", "Sitaw", "Malunggay")
gulay
```   
b. Add 2 additional vegetables after the last vegetables
in the list. What is the R script and its output?
```{r}
gulay <- append(gulay, list("Broccoli", "Mais"))
gulay
```   
c. Add 4 additional vegetables after index 5. How many
datapoints does your vegetable list have? What is the
R script and its output?
```{r}
gulay <- append(gulay, list("Patola", "Talong", "Sayote", "Kasoy"), after = 5)
gulay
```   
d. Remove the vegetables in index 5, 10, and 15. How many vegetables were left? Write the codes and its output.
```{r}
gulay <- gulay[-c(5, 10, 15)]
gulay
```   